Hypertension and microbiome

### 2019-06-10 articletwo.Rmd
Also salt pseq from centrifuge and only one genus level import

```{r lacto data frame}
pseq.genus.salt <- import_salt_pseq("data/phfinrisk_genus_all_drop50k_2018-11-16.RDs")

abund.genus.salt <- subset_taxa(pseq.genus.salt, Genus == "Lactobacillus") %>%
    abundances(., transform = "clr") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    setNames(tolower(replace.brackets(names(.))))

df.genus.salt <- meta(pseq.genus.salt) %>%
    tibble::rownames_to_column("id") %>%
    full_join(., abund.genus.salt, by = "id") %>%
    dplyr::mutate(salt_groups = relevel(factor(dplyr::ntile(dUNA, 3)), ref='1'),
                  lacto_groups = relevel(factor(dplyr::ntile(lactobacillus.bacteria, 3)), ref='1'))
```

@@

```{r abund salt lm continuous}
lm.lacto.duna <- lm(lactobacillus.bacteria ~ dUNA + BL_AGE + SEX, data = df.genus.salt)
lm.lacto.duna %>% tidy %>% mutate_if(is.numeric, round, 3) %>% kable
```

@@

```{r abund salt lm group}
lm.lacto.saltgroup <- lm(lactobacillus.bacteria ~ salt_groups + BL_AGE + SEX, data = df.genus.salt)
lm.lacto.saltgroup %>% tidy %>% mutate_if(is.numeric, round, 3) %>% kable
```

@@

Bartlett's test for equality of variance gives p = `r
bartlett.test(lactobacillus.bacteria ~ salt_groups, data =
df.genus.salt)$p.value`.

One-way test assuming normal distributions gives for equal mean p = `r
oneway.test(lactobacillus.bacteria ~ salt_groups, data =
df.genus.salt, var.equal = TRUE)$p.value`.

@@

```{r salt anova}
aov.lacto.saltgroup <- aov(lactobacillus.bacteria ~ salt_groups + BL_AGE + SEX, data = df.genus.salt)
aov.lacto.saltgroup %>% xtable %>% kable
```

@@

```{r lactobacillus RR}
calculateglm(df.genus.salt,
             modelstring = "%s ~ lactobacillus.bacteria + BL_AGE + SEX",
             filterstr = "lactobacillus") %>% 
    select(response, term, estimate, std.error, p.value) %>%
    mutate_if(is.numeric, round, 3) %>%
    kable
```

@@

```{r table map lactobacillus}
gvlma.table.plot(lm(MAP ~ lactobacillus.bacteria + BL_AGE + SEX, data = df.genus.salt))$table %>% kable
```

@@

```{r plot map lactobacillus, fig.width=12, fig.height=14}
gvlma.table.plot(lm(MAP ~ lactobacillus.bacteria + BL_AGE + SEX, data = df.genus.salt))$plot %>% plot
```

>>>>

```{r lacto data frame}
pseq.genus.salt <- pseq.genus %>%
    prune_samples(rownames(subset(meta(.), !is.na(NA.))), .) %>%
    prune_taxa(c("g_Lactobacillus", "g_Lactococcus"), .)

abund.genus.salt <- pseq.genus.salt %>%
    abundances(., transform = "clr") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id") %>%
    select(-g_Lactococcus)

df.genus.salt <- meta(pseq.genus.salt) %>%
    tibble::rownames_to_column("id") %>%
    full_join(., abund.genus.salt, by = "id") %>%
    dplyr::mutate(dUNA = myscale(NA.),
                  salt_groups = relevel(factor(dplyr::ntile(dUNA, 3)), ref='1'),
                  lacto_groups = relevel(factor(dplyr::ntile(g_Lactobacillus, 3)), ref='1'))
```

@@

```{r abund salt lm continuous}
lm.lacto.duna <- lm(g_Lactobacillus ~ dUNA + BL_AGE + SEX, data = df.genus.salt)
lm.lacto.duna %>% tidy %>% mutate_if(is.numeric, round, 3) %>% kable
```

@@

```{r abund salt lm group}
lm.lacto.saltgroup <- lm(g_Lactobacillus ~ salt_groups + BL_AGE + SEX, data = df.genus.salt)
lm.lacto.saltgroup %>% tidy %>% mutate_if(is.numeric, round, 3) %>% kable
```

@@

Bartlett's test for equality of variance gives p = `r
bartlett.test(g_Lactobacillus ~ salt_groups, data =
df.genus.salt)$p.value`.

One-way test assuming normal distributions gives for equal mean p = `r
oneway.test(g_Lactobacillus ~ salt_groups, data =
df.genus.salt, var.equal = TRUE)$p.value`.

@@

```{r salt anova}
aov.lacto.saltgroup <- aov(g_Lactobacillus ~ salt_groups + BL_AGE + SEX, data = df.genus.salt)
aov.lacto.saltgroup %>% xtable %>% kable
```

@@

```{r lactobacillus RR}
calculateglm(df.genus.salt,
             modelstring = "%s ~ g_Lactobacillus + BL_AGE + SEX",
             filterstr = "lactobacillus") %>% 
    select(response, term, estimate, std.error, p.value) %>%
    mutate_if(is.numeric, round, 3) %>%
    kable
```

@@

```{r table map lactobacillus}
gvlma.table.plot(lm(MAP ~ g_Lactobacillus + BL_AGE + SEX, data = df.genus.salt))$table %>% kable
```

@@

```{r plot map lactobacillus, fig.width=12, fig.height=14}
gvlma.table.plot(lm(MAP ~ g_Lactobacillus + BL_AGE + SEX, data = df.genus.salt))$plot %>% plot
```
